### 2014-03-16 src/analysis.Rnw
update graph

df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction)
df$sqr <- 1 - df$r.square
df$mult <- 1 - df$score.multiplier
df$type <- with(df, as.factor(
      ifelse(grepl('line',operator), 'line',
        ifelse(grepl('block',operator), 'block',
        ifelse(grepl('method',operator), 'method',
          ifelse(grepl('class',operator), 'class',
            ifelse(grepl('project',operator), 'project',
              'selection')))))))
df$sampling <- with(df,
      ifelse(grepl('op',strategy), 'operator(x)',
          ifelse(grepl('onelement',strategy), 'one(x)',
            ifelse(grepl('locelement',strategy), 'lines(x)',
              ifelse(grepl('withinelement',strategy), 'one(x)',
                ifelse(grepl('xceilperunit',strategy), 'ceil(x)',
                  ifelse(grepl('xpercentperunit',strategy), 'round(x)',
                    ifelse(grepl('xprobperunit',strategy), 'sample(x)',
strategy))))))))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
@
\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
\label{fig:fullimgsize}
\end{figure*}

>>>>

df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction)
df$sqr <- 1 - df$r.square
df$mult <- 1 - df$score.multiplier
df$type <- with(df, as.factor(
      ifelse(grepl('line',operator), 'line',
        ifelse(grepl('block',operator), 'block',
        ifelse(grepl('method',operator), 'method',
          ifelse(grepl('class',operator), 'class',
            ifelse(grepl('project',operator), 'project',
              ifelse(grepl('per_op',operator), 'x% operator',
              'operator selection'))))))))
df$sampling <- with(df,
          ifelse(grepl('onelement',strategy), 'one(x)',
            ifelse(grepl('locelement',strategy), 'lines(x)',
              ifelse(grepl('withinelement',strategy), 'one(x)',
                ifelse(grepl('xceilperunit',strategy), 'ceil(x)',
                  ifelse(grepl('xpercentperunit',strategy), 'round(x)',
                    ifelse(grepl('xprobperunit',strategy), 'sample(x)',
'other')))))))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
@
\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
\label{fig:fullimgsize}
\end{figure*}
